\section{Actor-critic}


In this problem we consider a realistic task in which a Sawyer robot needs to grasp a tool and use it to hammer in a nail. 
The agent controls a 4-DOF Sawyer robot with a continuous action space and receives environment states as observations.  
Providing dense rewards for real world problems is difficult, so in this environment the agent receives a sparse reward of 1.0 upon fully completing the task and no intermediate rewards. 
We will implement a general actor-critic algorithm that learns to solve the task with almost 100\% success rate. 
At each step the agent processes observations $o_t$, which consists of the environment states (e.g., pose of the robot gripper and hammer, etc.) from the last two environment steps. 
The full agent consists of:

\begin{itemize}
  \item The actor-critic algorithm utilizes critic networks $Q_{\theta^i}(o_t, a_t)$. This is implemented as the \textbf{Critic} class in \textbf{submission.py}. We use an ensemble 
  of $N$ different critic networks. Using an ensemble of critic networks can help reduce error in the Q-value estimates.
  \item Each critic network has a corresponding $target$ critic network $\bar{Q}_{\theta^i}(o_t, a_t)$., which is used for computing the Bellman targets for critic updates. 
  We use target critic networks, which are updated more slowly, to have a more stable target for learning.
  \item The final component of the algorithm is the Actor or policy $\pi_{\theta}(o_{t})$. This is implemented as the \textbf{Actor} class in \textbf{submission.py}. 
  You should familiarize yourself with these functions and their inputs and outputs. You should not modify any other files besides \textbf{submission.py}.
\end{itemize}


\begin{enumerate}[(a)]

  \input{02-actor-critic/01-bc}

  \input{02-actor-critic/02-actor-critic}

  \input{02-actor-critic/03-run}

\end{enumerate}



